Supplementary Informations to\\ Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels

### 2016-10-24 ion_pairing_SI.tex
add supplementary figure on 1H NMR of POH
Title: SI of...

%\title{Supramolecular crocodile line controls the rheological properties of polyelectrolytes hydrogels}
\title{Supplementary Informations to Ion pairing controls rheological properties of ``crocodile-line'' polyelectrolyte hydrogels}
%\title{Ion pairing in crocodile line hydrogels controls rheological properties}
%\title{In crocodile line hydrogels ion pairing controls rheological properties}
%\title{Controlling the rheological properties of well-defined polyelectrolytes hydrogels by fine tuning their ion pairing process}

@@

SEC analyses were carried out on ca \SI{5}{\milli\gram\per\milli\litre} solutions of each polymer in DMSO LiBr (\SI{0.01}{M}), using a MALVERN VISCOTEK 430  system equipped with three PSS Gram columns (Polyester Copolymer Network) set in series at \SI{80}{\celsius}, coupled to a Viscotek HT-GPC Module 350 A (refractive and viscosimeter) detector (at \SI{80}{\celsius}). The polydispersity indexes (PDI = Mw/Mn) of the samples were derived from the RI signal by a universal calibration curve by pullulan. The number-average molar masses (Mn) were calculated from RI signals with the OmniSEC 4.6 software.

@@

@@

\begin{figure}
\includegraphics{frequency.pdf}
\caption{Storage modulus $G^\prime$ ($\bullet$) and loss modulus $G^{\prime\prime}$ ($\square$) measured through oscillatory shear experiments plotted against the frequency $f$. The moieties change with rows and the counterions with columns. The fixed strain amplitude is $\gamma=0.1\%$. All samples are at 7.4~\%~wt }
\label{fig:frequency}
\end{figure}

>>>>

\title{Supplementary Informations to\\ Ion pairing controls rheological properties of ``processionary'' polyelectrolyte hydrogels}

@@

SEC analyses were carried out on ca \SI{5}{\milli\gram\per\milli\litre} solutions of each polymer in DMSO LiBr (\SI{0.01}{M}), using a MALVERN VISCOTEK 430  system equipped with three PSS Gram columns (Polyester Copolymer Network) set in series at \SI{80}{\celsius}, coupled to a Viscotek HT-GPC Module 350 A (refractive and viscosimeter) detector (at \SI{80}{\celsius}). The dispersity (\DJ = Mw/Mn) of the samples were derived from the RI signal by a universal calibration curve by pullulan. The number-average molar masses (Mn) were calculated from RI signals with the OmniSEC 4.6 software.

@@

\begin{figure}
\includegraphics[width=\textwidth]{POH_1H_NMR.png}
\caption{1H NMR of POH in deuterated methanol, with signal attribution. Calibration of the integrals intensity, relative to the distinct chain-end signals (a and b, 6 protons each), allows us to determine polymer chain length $n$ (here, considering integration of signal d, $n=63$)}
\end{figure}

@@

\begin{figure}
\includegraphics{frequency.pdf}
\caption{Storage modulus $G^\prime$ ($\bullet$) and loss modulus $G^{\prime\prime}$ ($\square$) measured through oscillatory shear experiments plotted against the frequency $f$. The moieties change with rows and the counterions with columns. The fixed strain amplitude is $\gamma=0.1\%$. All samples are at 7.4~wt\%. }
\label{fig:frequency}
\end{figure}
